Volatility and the Buyback Anomaly: Interactive Tool

### 2016-05-12 index.Rmd
industries

<!--
 Copyright 2015, INSEAD
 by T. Evgeniou, Enric Junque de Fortuny, Nick Nassuphis, Theo Vermaelen 
 Dual licensed under the MIT or GPL Version 2 licenses.  -->

@@

@@

run_shiny_tool = 0

@@

source("interactive_tool_files/lib_helpers.R", chdir=TRUE)
source("interactive_tool_files/ff_industries_sic.R")
source("Paper_global_parameters.R")
source("interactive_tool_files/heatmapOutput.R")

>>>>

@@

```{r, eval=TRUE, echo = FALSE,message=FALSE}
# Copyright 2015, INSEAD
# by T. Evgeniou, Enric Junque de Fortuny, Nick Nassuphis, Theo Vermaelen 
# Dual licensed under the MIT or GPL Version 2 licenses.  
```

@@

run_shiny_tool = 1

@@

source("interactive_tool_files/lib_helpers.R", chdir=TRUE)
source("interactive_tool_files/ff_industries_sic.R")
source("Paper_global_parameters.R")
source("interactive_tool_files/heatmapOutput.R") 
source("interactive_tool_files/ff_industries_sic.R")
